---
title: "Hepner_et_al_2018_eDNA"
author: "Megan Hepner"
date: "February 26, 2018"
output: html_document
---

```{r librarys}
knitr::opts_chunk$set(echo = TRUE)

library(ggplot2)
library(gridExtra) #grid.arrange
library(tidyverse)
library(VennDiagram)

```

# Dive Log 

Site: Looe Key (Buoy 31)
Date: May 23rd 2016 
Latitude: 24.32499 
Longitude: -81.24971
Max dive depth: 45 ft 
Underwater Visibility: 40 ft 
Water Temperature (F): 84
Current: None 
Divers: Megan Hepner (USF) & Lonny Anderson (NOAA)

Site: Western Sambo (Buoy "O")
Date: May 23rd 2016
Latitude: 24.29007
Longitude: -81.42225 
Max dive depth: 57 ft 
Underwater Visibility: 20 ft 
Water Temperature (F): 82
Current: None
Divers: Megan Hepner (USF) & Lonny Anderson (NOAA)

Site: Molasses Reef (Buoy 27)
Date: May 25th 2016
Latitude: 25.00439
Longitude: -80.22468
Max dive depth: 50 ft 
Underwater Visibility: 30 ft 
Water Temperature (F): 85 
Current: Moderate-High 
Divers: Megan Hepner (USF) & Lonny Anderson (NOAA)

```{r read dataset}

dive_surveys = read_csv("may_2016_dive_surveys.csv")

#Looe Key 18 families, 36 species
#Western Sambo 13 families, 38 species 
#Molasses Reef 14 families, 30 species 

MR = dive_surveys %>% 
  select(molasses_reef, family_scientific_name, scientific_name) %>%
  filter(molasses_reef != 0)
  length(unique(MR$family_scientific_name))
  
#Remove NA's 
  dive_surveys_cleaned = dive_surveys %>%
    filter(scientific_name != "NA") #56 species 
  length(unique(dive_surveys_cleaned$family_scientific_name)) #19 families 

```

```{r Venn diograms}

LK_VD = draw.pairwise.venn(
  area1 = ,
  area2 = ,
  category = c("Visual Surveys", "eDNA 12S"),
  fill = c("yellow","blue"))

WS_VD
MR_VD 

```
